Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.

### 2024-02-27 index.qmd
add all

---
title: Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.
author:
  - name: Simon Oiry
    orcid: 0000-0001-7161-5246
    corresponding: true
    email: oirysimon@gmail.com
    roles:
      - Investigation
      - Writing
      - Data acquisition
    affiliations:
      - Nantes University
  - name: Bede Ffinian Rowe Davies
    corresponding: false
    roles: 
      - Investigation
      - Data acquisition
      - Revision
    affiliations:
      - Nantes University
  - name: Pierre Gernez
    corresponding: false
    roles: 
      - Investigation
      - Data acquisition
      - Revision
    affiliations:
      - Nantes University
  - name: Ana I. Sousa
    corresponding: false
    roles:
      - Data acquisition
      - Revision
    affiliations:
      - Aveiro University
  - name: Philippe Rosa
    corresponding: false
    roles: 
      - Data acquisition
      - Revision
    affiliations:
      - Nantes University
  - name: Maria Laura Zoffoli
    corresponding: false
    roles: 
      - Data acquisition
      - Revision
    affiliations:
      - CNR ISMAR
  - name: Guillaume Brunier
    corresponding: false
    roles: 
      - Data acquisition
      - Revision
    affiliations:
      - JeSaisPas
  - name: Laurent Barillé
    corresponding: false
    roles: 
      - Investigation
      - Data acquisition
      - Revision
    affiliations:
      - Nantes University
keywords:
  - Drone
  - Remote Sensing
abstract: |
  Coastal areas host seagrass meadows, which offer crucial ecosystem services including erosion control and carbon sequestration. However, these areas are increasingly impacted by human activities, leading to seagrass decline and habitat fragmentation. In situ surveys, traditionally performed to monitor these ecosystems face limitations on temporal and spatial coverage, particularly in intertidal zones, prompting the use of satellite data within monitoring programs. Yet, satellite remote sensing struggles with spatial and spectral resolution, making it difficult to discriminate seagrass from other macrophytes in highly heterogenous meadows. To address these challenges, drone images acquired with multi-spectral sensors offer a promising solution. This study focuses on using drones acquisitions for mapping intertidal macrophytes, effectively discriminating between seagrass and green macroalgae. Ten drone flights were conducted at two different altitudes (12m and 120m) across diverse European habitats in France and Portugal. Low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discrimintate among 5 intertidal vegetation classes. Drone mapping demonstrated an overall accuracy of 94% across all the sites and images, covering a total area of 467 000 m². The model exhibited an accuracy of 96.4% in identifying seagrass.
plain-language-summary: |
  This study demonstrates the efficacy of using drones equipped with multi-spectral sensors for mapping intertidal macrophytes, particularly seagrass, overcoming limitations of traditional in situ surveys and satellite remote sensing, with a Deep Learning classifier achieving 94% overall accuracy across diverse European habitats, and 96.4% accuracy specifically in identifying seagrass.

key-points:
  - An intertidal vegetation classifier has been built to be used across different study sites without losing classification accuracy. 
  - Neural Network made to accuratly discriminates intertidal seagrasses from green algae (chlorophyceae)
date: last-modified
number-sections: true
---

@@

```{r}
#| cache: false
#| echo: false
#| warning: false

@@

```{r}
#| cache: true
#| echo: false
#| warning: false
#| eval: true

@@

```{r}
#| echo: false
#| warning: false
#| cache: true

>>>>

---
title: Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.
author:
  - name: Simon Oiry
    orcid: 0000-0001-7161-5246
    corresponding: true
    email: oirysimon@gmail.com
    roles:
      - Investigation
      - Writing
      - Data acquisition
    affiliations:
      - Nantes University
  - name: Bede Ffinian Rowe Davies
    corresponding: false
    roles: 
      - Investigation
      - Data acquisition
      - Revision
    affiliations:
      - Nantes University
  - name: Pierre Gernez
    corresponding: false
    roles: 
      - Investigation
      - Data acquisition
      - Revision
    affiliations:
      - Nantes University
  - name: Ana I. Sousa
    corresponding: false
    roles:
      - Data acquisition
      - Revision
    affiliations:
      - Aveiro University
  - name: Philippe Rosa
    corresponding: false
    roles: 
      - Data acquisition
      - Revision
    affiliations:
      - Nantes University
  - name: Maria Laura Zoffoli
    corresponding: false
    roles: 
      - Data acquisition
      - Revision
    affiliations:
      - CNR ISMAR
  - name: Guillaume Brunier
    corresponding: false
    roles: 
      - Data acquisition
      - Revision
    affiliations:
      - JeSaisPas
  - name: Laurent Barillé
    corresponding: false
    roles: 
      - Investigation
      - Data acquisition
      - Revision
    affiliations:
      - Nantes University
keywords:
  - Drone
  - Remote Sensing
abstract: |
  Coastal areas host seagrass meadows, which offer crucial ecosystem services including erosion control and carbon sequestration. However, these areas are increasingly impacted by human activities, leading to seagrass decline and habitat fragmentation. In situ surveys, traditionally performed to monitor these ecosystems face limitations on temporal and spatial coverage, particularly in intertidal zones, prompting the use of satellite data within monitoring programs. Yet, satellite remote sensing struggles with spatial and spectral resolution, making it difficult to discriminate seagrass from other macrophytes in highly heterogenous meadows. To address these challenges, drone images acquired with multi-spectral sensors offer a promising solution. This study focuses on using drones acquisitions for mapping intertidal macrophytes, effectively discriminating between seagrass and green macroalgae. Ten drone flights were conducted at two different altitudes (12m and 120m) across diverse European habitats in France and Portugal. Low altitude flights were used to train a Deep Learning classifier based on Neural Networks to discrimintate among 5 intertidal vegetation classes. Drone mapping demonstrated an overall accuracy of 94% across all the sites and images, covering a total area of 467 000 m². The model exhibited an accuracy of 96.4% in identifying seagrass.
plain-language-summary: |
  This study demonstrates the efficacy of using drones equipped with multi-spectral sensors for mapping intertidal macrophytes, particularly seagrass, overcoming limitations of traditional in situ surveys and satellite remote sensing, with a Deep Learning classifier achieving 94% overall accuracy across diverse European habitats, and 96.4% accuracy specifically in identifying seagrass.
key-points:
  - An intertidal vegetation classifier has been built to be used across different study sites without losing classification accuracy. 
  - Neural Network made to accuratly discriminates intertidal seagrasses from green algae (chlorophyceae)
date: last-modified
number-sections: true
---

@@

```{r my_comma}
#| cache: false
#| echo: false
#| warning: false

@@

```{r df_training}
#| cache: true
#| echo: false
#| warning: false
#| eval: true

@@

```{r count_validation_pixel}
#| echo: false
#| warning: false
#| cache: true
